\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2018-09-28 redaction/dhp_travail.tex
typo
typo sur le ö de Görg

\title{\textsc{International Transport costs:\\New Findings from modeling additive costs}\thanks{We are grateful to Olger Görg, S\'{e}bastien Jean, Vincent Vicard for their insightful comments. The paper has greatly benefited from remarks from the participants at ETSG 17\textsuperscript{th} (Helsinki), DEGIT XXII (Paris), seminars at the Universites of California-Irvine, Paris-Dauphine, Paris-I, Nancy and the the Kiel Institute for the World Economy.
Finally, any remaining errors are ours.
This paper was partly funded by an University grant from Lille-I University.
It features an online appendix containing additional results and available on the authors' websites.}}

>>>>

\title{\textsc{International Transport costs:\\New Findings from modeling additive costs}\thanks{We are grateful to Olger G\"{o}rg, S\'{e}bastien Jean, Vincent Vicard for their insightful comments. The paper has greatly benefited from remarks from the participants at ETSG 17\textsuperscript{th} (Helsinki), DEGIT XXII (Paris), seminars at the Universites of California-Irvine, Paris-Dauphine, Paris-I, Nancy and the the Kiel Institute for the World Economy.
Finally, any remaining errors are ours.
This paper was partly funded by an University grant from Lille-I University.
It features an online appendix containing additional results and available on the authors' websites.}}
